Trade Reviews

### 2019-04-07 tradeReview.Rmd
Adjusted z_scores, free agent options

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
```

@@

rosters %>% 
  filter(grepl('Tom|Christopher',manager)) %>% 
  select(manager, name_full, display_position) -> roster_players

@@

roster_players %>% 
  left_join(draft_results, by = c("name_full" = "player")) %>% 
  left_join(projections, by = c("name_full" = "Name")) -> trade_df

trade_df %>% saveRDS("data/tradeReview_20190405.Rds")

trade_df %>% 
  mutate(z_sum = round(z_sum)) %>% 
  arrange(z_sum %>% desc, pick) %>% 
  write_csv("data/tradeReview_20190405.csv")
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(glue)
library(plotly)
```

@@

@@

projections$Name[projections$Name == 'Enrique Hernandez'] <- "Kike Hernandez"
projections$Name[projections$Name == 'Peter Alonso'] <- "Pete Alonso"
projections$Name[projections$Name == 'Joshua James'] <- "Josh James"

rosters %>% 
  left_join(draft_results, by = c("name_full" = "player")) %>% 
  full_join(projections, by = c("name_full" = "Name")) %>% 
  mutate(team = if_else(is.na(team),"Free Agent",team),
         team = fct_reorder(team, z_sum)) -> rosters_with_projections

rosters_with_projections %>% 
  saveRDS("data/rosters_with_projections_20190405.Rds")
```

#### Evaluate trade options
```{r}
rosters_with_projections %>% 
  filter(grepl('Tom|Christopher',manager)) %>% 
  select(manager, name_full, display_position, pick, z_sum) %>%  
  mutate(z_sum = round(z_sum)) %>% 
  arrange(z_sum %>% desc, pick) %>% 
  View()
```

## Other research

```{r}
rosters_with_projections %>% 
  mutate(z_sum = round(z_sum)) %>% 
  ggplot(aes(x=team,y=z_sum,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
  coord_flip() -> p

ggplotly(p)

rosters_with_projections %>% 
  filter(!type == 'NA', !team == 'Free Agent') %>%
  ggplot(aes(x=type,y=z_sum)) +
  geom_boxplot()

rosters_with_projections %>% 
  filter(!type == 'NA', !team == 'Free Agent') %>%
  group_by(type) %>% 
  summarize(adj = median(z_sum)) -> z_sum_adj

rosters_with_adj_projections <- rosters_with_projections %>% 
  filter(!type == 'NA') %>% 
  mutate(zar = if_else(type=="batter",
                       z_sum-z_sum_adj$adj[z_sum_adj$type=="batter"],
                       z_sum-z_sum_adj$adj[z_sum_adj$type=="pitcher"]))

rosters_with_adj_projections %>% 
  ggplot(aes(x=type,y=zar)) +
  geom_boxplot()

rosters_with_adj_projections %>% 
  mutate(zar = round(zar)) %>% 
  ggplot(aes(x=team,y=zar,color=type)) +
  geom_jitter(aes(text=glue("{name_full} - {display_position}", color=type))) +
  coord_flip() -> z

ggplotly(z)

rosters_with_adj_projections %>% 
  filter((team == 'Free Agent' & zar >=0) | (grepl("Plouffe",team) & zar < 0)) %>% 
  arrange(zar %>% desc) %>% 
  select(name_full, display_position, type, zar) %>% 
  View()
```
